---
title: "Case Study"
author: Kiana chan 
output: html_document
---




```{r setup, include = FALSE}
library(tidyverse)
library(leaflet)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load a dataset 
```{r}
data("nyc_airbnb")
```

What kinds of questions might you be interested in asking using this dataset? 
*How many rentals are there? or what type? in what places? 
* is price correlated with review score? 
* which neighborhood is most popular? most expensive? 
* which neighborhood has highest reviews? 
* is availability related to price? 
* is room type related to neighborhood? 
* is length of stay related to neighborhood group(borough)? 
*which neighborhood has the highest reviews?

```{r}
nyc_airbnb = nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```

Price and neighborhood - how much does this distribution vary by room type? 
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
arrange(mean_price)

nyc_airbnb %>% 
    filter(borough == "Manhattan", price <= 1000) %>% 
    mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
    ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() +
  facet_grid(. ~ room_type)
```


Price vs. Loation 

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>%  #random sample of 5k in your 40k dataset 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)
```



Price and roomtype 
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = review_scores_location, y = price)) + 
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood 
coord flip flips the axis 
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
arrange(mean_price)

nyc_airbnb %>% 
    filter(borough == "Manhattan", price <= 1000) %>% 
    mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
    ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```
Let's try to count things: 

```{r}
nyc_airbnb %>% 
  count(borough)
```
```{r}
nyc_airbnb %>% 
  count(borough, room_type)
```
```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)
```
another way to make the same table above 
```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
      names_from = room_type,
      values_from = n
  )
```


## Let's retry leaflet (for mapping)


```{r}
pal = colorNumeric("viridis", NULL)

nyc_airbnb %>%
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(price))

```

